### 2024-03-25 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

## Workflow

::: {.sourceClojure}
```clojure
(ns index
  (:require [tablecloth.api :as tc]
            [tech.v3.datatype.datetime :as datetime]
            [clojure.string :as str]
            [scicloj.noj.v1.vis.hanami :as hanami]
            [aerial.hanami.templates :as ht]
            [fastmath-clustering.core :as clustering]
            [scicloj.kindly.v4.kind :as kind]))
```
:::

@@

@@

::: {.sourceClojure}
```clojure
(def processed-trips
  (-> raw-trips
      (tc/add-column :hour (fn [trips]
                             (->> trips
                                  :started_at
                                  (datetime/long-temporal-field :hours))))
      (tc/select-rows (fn [row]
                        (->> coord-colnames
                             (map row)
                             (every? some?))))))
```
:::

@@

@@

<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>1</td><td>11750</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>11702</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>81</td><td>11208</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>6</td><td>11195</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>52</td><td>10907</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>

>>>>

## Setup

::: {.sourceClojure}
```clojure
(ns index
  (:require [tablecloth.api :as tc]
            [clojure.math :as math]
            [tech.v3.datatype.datetime :as datetime]
            [clojure.string :as str]
            [scicloj.noj.v1.vis.hanami :as hanami]
            [aerial.hanami.templates :as ht]
            [fastmath-clustering.core :as clustering]
            [geo
             [geohash :as geohash]
             [jts :as jts]
             [spatial :as spatial]
             [io :as geoio]
             [crs :as crs]]
            [scicloj.kindly.v4.kind :as kind]
            [scicloj.kindly.v4.api :as kindly])
  (:import (org.locationtech.jts.geom Geometry Point Polygon Coordinate)
           (org.locationtech.jts.geom.prep PreparedGeometry
                                           PreparedLineString
                                           PreparedPolygon
                                           PreparedGeometryFactory)))
```
:::

## Reading the data

@@

## Coordinate conversions

The datasets uses the [WGS84](https://en.wikipedia.org/wiki/World_Geodetic_System)
coordinate system, representing latitude and longitued over the globe.
[EPSG:4326](https://epsg.io/4326)

For metric computations we need to convert them to a coordinate system
which is locally correct in terms of distances in a region around Chicago:
NAD83 / Illinois East
[EPSG:26971](https://epsg.io/26971-1742)

::: {.clay-dataset}
United States (USA) - Oregon and Washington. [1 3]:

|   Center coordinates |                             Projected bounds |                   WGS84 bounds |
|----------------------|----------------------------------------------|--------------------------------|
| [316133.6 345590.74] | [[216692.35 43649.23] [416809.98 648476.24]] | [[-89.27 37.06] [-87.02 42.5]] |

::: {.sourceClojure}
```clojure
(def crs-transform
  (geo.crs/create-transform (geo.crs/create-crs 4326)
                            (geo.crs/create-crs 26971)))
```
:::

::: {.sourceClojure}
```clojure
(defn wgs84->Chicago
  "Transforming latitude-longitude coordinates
  to local Euclidean coordinates around Seattle."
  [geometry]
  (geo.jts/transform-geom geometry crs-transform))
```
:::

::: {.sourceClojure}
```clojure
(defn lat-lng->local-coords [lat lng]
  (-> (geo.jts/coordinate -89.27 37.06)
      geo.jts/point
      wgs84->Chicago
      geo.jts/coord
      ((fn [^Coordinate coord]
         [(.getX coord)
          (.getY coord)]))))
```
:::

Example:

::: {.sourceClojure}
```clojure
(delay
  (lat-lng->local-coords -89.27 37.06))
```
:::

::: {.printedClojure}
```clojure
[216692.34803057025 44059.50658557552]

```
:::

## Preprocessing

@@

::: {.sourceClojure}
```clojure
(def processed-trips
  (-> raw-trips
      (tc/add-column :hour (fn [trips]
                             (->> trips
                                  :started_at
                                  (datetime/long-temporal-field :hours))))
      (tc/select-rows (fn [row]
                        (->> coord-colnames
                             (map row)
                             (every? some?))))
      (tc/map-columns :start-local-coords [:start_lat :start_lng] lat-lng->local-coords)
      (tc/map-columns :end-local-coords [:end_lat :end_lng] lat-lng->local-coords)
      (tc/map-columns :start-local-x [:start-local-coords] first)
      (tc/map-columns :start-local-y [:start-local-coords] second)
      (tc/map-columns :end-local-x [:end-local-coords] first)
      (tc/map-columns :end-local-y [:end-local-coords] second)))
```
:::

## Comparing Eucledian (L2) distances in global and local coordinates

TODO

## Basic analysis and visualization

@@

## Clustering

@@

<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>map-0</th><th>hours-0</th></tr></thead><tbody><tr><td>92</td><td>12495</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>39</td><td>12190</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>12107</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>49</td><td>11723</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>45</td><td>11702</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"png"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
